A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2024-01-29 manuscript/manuscript.Rmd

```bash
sudo apt update && sudo apt install docker.io -y  # 30 sec
sudo docker run -it --platform linux/amd64 mziemann/enrichment_recipe Rscript -e 'rmarkdown::render("example.Rmd")'
docker cp $(docker ps -aql):/enrichment_recipe/example.html . # instant
firefox example.html
```
<p style="text-align: center;">
*Box 1. Linux shell commands to reproduce a transcriptome and enrichment analysis using a Docker image.*
</p>

>>>>

```bash
sudo apt update && sudo apt install docker.io -y  # 30 sec
sudo docker run --platform linux/amd64 mziemann/enrichment_recipe Rscript -e 'rmarkdown::render("example.Rmd")' # 150 sec
docker cp $(docker ps -aql):/enrichment_recipe/example.html . # instant
firefox example.html
```
<p style="text-align: center;">
*Box 1. Linux shell commands to reproduce a transcriptome and enrichment analysis using a Docker image.*
</p>
